The Weakly Nonlinear Magnetorotational Instability

### 2016-09-05 paper/widegap_mri_paper.tex
changed sign of nonlinear terms in appendix so they represent rhs
updated journal abbreviations

\beq
N_2^{\Psi}  = J(\Psi_1, \frac{1}{r^2} \nabla^2 \Psi_1) + J(\Psi_1, -\frac{2}{r^3}\partial_r\Psi_1)
- \frac{2}{\beta} J (A_1, \frac{1}{r^2} \nabla^2 A_1) - \frac{2}{\beta} J(A_1, -\frac{2}{r^3} \partial_r A_1) - \frac{2}{r} u_1 \partial_z u_1 + \frac{2}{\beta} \frac{2}{r} B_1 \partial_z B_1
\eeq

\beq
\begin{split}
N_2^{u} = \frac{1}{r} J\left(\Psi_1, u_1\right) - \frac{1}{r} \frac{2}{\beta} J\left(A_1, B_1\right) + \frac{1}{r^2} u_1 \partial_z \Psi_1 - \frac{2}{\beta}\frac{1}{r^2} B_1 \partial_z A_1
\end{split}
\eeq

\beq
N_2^A = -\frac{1}{r} J\left(A_1, \Psi_1\right)
\eeq

\beq
N_2^B = -\frac{1}{r} J\left(A_1, u_1\right) - \frac{1}{r} J\left(B_1, \Psi_1\right) - \frac{1}{r^2} B_1 \partial_z \Psi_1 + \frac{1}{r^2} u_1 \partial_z A_1
\eeq

\beq
\begin{split}
N_3^{\Psi} & = J(\Psi_1, \frac{1}{r^2} \nabla^2 \Psi_2) + J(\Psi_2, \frac{1}{r^2} \nabla^2\Psi_1) + 2 J (\Psi_1, \frac{1}{r^2}\partial_Z\partial_z \Psi_1) + J(\Psi_1, -\frac{2}{r^3}\partial_r \Psi_2) + J(\Psi_2, -\frac{2}{r^3}\partial_r \Psi_1) \\
& + \widetilde{J}(\Psi_1, \frac{1}{r^2} \nabla^2 \Psi_1) + \widetilde{J} (\Psi_1, -\frac{2}{r^3}\partial_r \Psi_1) - \frac{2}{\beta} J(A_1, \frac{1}{r^2}\nabla^2 A_2) - \frac{2}{\beta} J(A_2, \frac{1}{r^2}\nabla^2 A_1) - \frac{4}{\beta} J(A_1, \frac{1}{r^2}\partial_Z\partial_z A_1) \\ & - \frac{2}{\beta} J(A_1, -\frac{2}{r^3} \partial_r A_2 ) 
 - \frac{2}{\beta} J(A_2, -\frac{2}{r^3} \partial_r A_1) - \frac{2}{\beta} \widetilde{J} (A_1, \frac{1}{r^2} \nabla^2 A_1) - \frac{2}{\beta} \widetilde{J} (A_1, -\frac{2}{r^3} \partial_r A_1) \\
& - \frac{2}{r} u_1 \partial_z u_2 - \frac{2}{r} u_2 \partial_z u_1 - \frac{2}{r} u_1 \partial_Z u_1 + \frac{2}{\beta}\frac{2}{r} B_1\partial_z B_2 + \frac{2}{\beta}\frac{2}{r} B_2 \partial_z B_1 + \frac{2}{\beta} \frac{2}{r} B_1 \partial_Z B_1
\end{split}
\eeq

\beq
\begin{split}
N_3^u & = \frac{1}{r}J\left(\Psi_1, u_2\right) + \frac{1}{r}J\left(\Psi_2, u_1\right) + \frac{1}{r}\widetilde{J} \left(\Psi_1, u_1\right) - \frac{1}{r}\frac{2}{\beta} J\left(A_1, B_2\right) - \frac{1}{r} \frac{2}{\beta} J\left(A_2, B_1\right) - \frac{1}{r}\frac{2}{\beta}\widetilde{J}\left(A_1, B_1\right) \\
& + \frac{1}{r^2} u_1\partial_z \Psi_2 + \frac{1}{r^2} u_2 \partial_z \Psi_1 + \frac{1}{r^2} u_1 \partial_Z \Psi_1 - \frac{2}{\beta} \frac{1}{r^2} B_1 \partial_z A_2 - \frac{2}{\beta} \frac{1}{r^2} B_2 \partial_z A_1 - \frac{2}{\beta} \frac{1}{r^2} B_1 \partial_Z A_1
\end{split}
\eeq

\beq
N_3^A = -\frac{1}{r} J\left(A_1, \Psi_2\right) - \frac{1}{r}J\left(A_2, \Psi_1\right) - \frac{1}{r} \widetilde{J}\left(A_1, \Psi_1\right)
\eeq

\beq
\begin{split}
N_3^B & = - \frac{1}{r} J\left(A_1, u_2\right) - \frac{1}{r} J\left(A_2, u_1\right) - \frac{1}{r}\widetilde{J}\left(A_1, u_1\right) - \frac{1}{r} J\left(B_1, \Psi_2\right) - \frac{1}{r} J\left(B_2, \Psi_1\right) - \frac{1}{r} \widetilde{J} \left(B_1, u_1\right) \\ & - \frac{1}{r^2} B_1\partial_z \Psi_2 - \frac{1}{r^2} B_2 \partial_z \Psi_1 - \frac{1}{r^2} B_1 \partial_Z \Psi_1 + \frac{1}{r^2} u_1 \partial_z A_2 + \frac{1}{r^2} u_2 \partial_z A_1 + \frac{1}{r^2} u_1 \partial_Z A_1
\end{split}
\eeq

@@

\bibitem[{Aranson \& Kramer(2002)}]{Aranson:2002}
Aranson, I.S. \& Kramer, L., 2002, Rev. Mod. Phys. 74, 99

@@

\bibitem[{Balbus \& Hawley(1991)}]{Balbus:1991vs}
Balbus, S A and Hawley, J F, 1991, The Astrophysical Journal, 376, 214

@@

\bibitem[{Chandrasekhar(1960)}]{Chandrasekhar:1960wh}
Chandrasekhar, S. 1960, Proceedings of the National Academy of Sciences of the United States of America, 46, 253

@@

\bibitem[{Cross \& Hohenberg(1993)}]{Cross:1993el}
Cross, M. C., \& Hohenberg, P. C., 1993, Rev. Mod. Phys. 65, 851

\bibitem[{Ebrahimi et al.(2009)}]{Ebrahimi:2009ey}
Ebrahimi, F., Prager, S.C., Schnack, D.D

@@

\bibitem[{Gissinger et al.(2011)}]{Gissinger:2011td}
Gissinger, C, Ji, H, Goodman, J, 2011, Phys. Rev. E 84, 026308

\bibitem[{Gissinger et al.(2012)}]{Gissinger:2012gc}
Gissinger, C, Goodman, J, \& Ji, H, 2012, Physics of Fluids 24, 074109

@@

\bibitem[{Hollerbach(2009)}]{Hollerbach:2009ig}
Hollerbach, R, Proc. R. Soc. A, 2009, 465, 2107

\bibitem[{Hollerbach \& R\"udiger(2005)}]{Hollerbach:2005tr}
Hollerbach, R. \& R\"udiger, G., 2005, Phys. Rev. Lett. 95, 124501

@@

\bibitem[{Ji et al.(2001)}]{Ji:2001kd}
Ji, H, Goodman, J, Kageyama, A, Mon. Not. R. Astron. Soc., 2001, 325, 1

@@

\bibitem[{Kirillov \& Stefani(2013)}]{Kirillov:2013}
Kirillov, O, \& Stefani, F, 2013, Phys. Rev. Lett. 111, 061103

\bibitem[{Knobloch \& Julien(2005)}]{Knobloch:2005ba}
Knobloch, E, Julien K, 2005, Physics of Fluids, 17, 094106

@@

\bibitem[{Liu et al.(2006)}]{Liu:2006}
Liu, W, Goodman, J, Herron, I, and Ji, H, 2006, Phys. Rev. E 74, 056302

\bibitem[{Lopez \& Marques(2005)}]{Lopez:2005} 
Lopez, J.~M., \& Marques, F.\ 2005, Physica D, 211, 168

@@

\bibitem[{Parker \& Krommes(2013)}]{Parker:2013hy}
Parker, J.B. \& Krommes, J.A., 2013, Phys of Plasmas 20, 100703

@@

\bibitem[{Recktenwald et al.(1993)}]{Recktenwald:1993}
Recktenwald, A., L\"ucke, M., M\"uller, H.W., 1993, Phys Rev E 48, 4444

\bibitem[{R\"udiger \& Hollerbach(2007)}]{Rudiger:2007}
R\"udiger, G, \& Hollerbach, R, Phys. Rev. E 76, 068301

\bibitem[{Schartman et al.(2009)}]{Schartman:2009df}
Schartman, E, Ji, H, Burin, M J, Rev Sci Instrum, 2009, 80, 024501

\bibitem[{Shakura \& Sunyaev(1973)}]{Shakura:1973wg}
Shakura, N I and Sunyaev, R A, Astronomy \& Astrophysics, 1973, 24, 337

\bibitem[{Sisan et al.(2004)}]{Sisan:2004ig}
Sisan, D R, Mujica, N, Tillotson, W A, Huang Y-M, Dorland, W, Hassam, A B, Antonsen, T M, Lathrop, D P, Phys Rev Lett, 2004, 93, 11

\bibitem[{Stefani et al.(2006)}]{Stefani:2006iv}
Stefani, F, Gundrum, T, Gerbeth, G, R\"udiger, G, Schultz, M, Szklarski, J, Hollerbach, R, Phys Rev Lett, 2006, 97, 184502

\bibitem[{Stefani et al.(2009)}]{Stefani:2009hp}
Stefani, F, Gerbeth, G, Gundrum, T, Hollerbach, R, Priede, J, R\"udiger, G, and Szklarski, J, Phys Rev E, 80, 066303

@@

\bibitem[{Umurhan et al.(2007a)}]{Umurhan:2007dz}
Umurhan, O.M., Regev, O., Menou, K., 2007, Phys. Rev. Letters, 98, 034501

\bibitem[{Umurhan et al.(2007b)}]{Umurhan:2007hs}
Umurhan, O.M., Regev, O., Menou, K., 2007, Phys. Rev. E, 76, 036310

>>>>

\beq
N_2^{\Psi}  = -J(\Psi_1, \frac{1}{r^2} \nabla^2 \Psi_1) - J(\Psi_1, -\frac{2}{r^3}\partial_r\Psi_1)
+ \frac{2}{\beta} J (A_1, \frac{1}{r^2} \nabla^2 A_1) + \frac{2}{\beta} J(A_1, -\frac{2}{r^3} \partial_r A_1) + \frac{2}{r} u_1 \partial_z u_1 - \frac{2}{\beta} \frac{2}{r} B_1 \partial_z B_1
\eeq

\beq
\begin{split}
N_2^{u} = -\frac{1}{r} J\left(\Psi_1, u_1\right) + \frac{1}{r} \frac{2}{\beta} J\left(A_1, B_1\right) - \frac{1}{r^2} u_1 \partial_z \Psi_1 + \frac{2}{\beta}\frac{1}{r^2} B_1 \partial_z A_1
\end{split}
\eeq

\beq
N_2^A = \frac{1}{r} J\left(A_1, \Psi_1\right)
\eeq

\beq
N_2^B = \frac{1}{r} J\left(A_1, u_1\right) - \frac{1}{r} J\left(\Psi_1, B_1\right) + \frac{1}{r^2} B_1 \partial_z \Psi_1 - \frac{1}{r^2} u_1 \partial_z A_1
\eeq

\beq
\begin{split}
N_3^{\Psi} & = -J(\Psi_1, \frac{1}{r^2} \nabla^2 \Psi_2) - J(\Psi_2, \frac{1}{r^2} \nabla^2\Psi_1) - 2 J (\Psi_1, \frac{1}{r^2}\partial_Z\partial_z \Psi_1) - J(\Psi_1, -\frac{2}{r^3}\partial_r \Psi_2) - J(\Psi_2, -\frac{2}{r^3}\partial_r \Psi_1) \\
& - \widetilde{J}(\Psi_1, \frac{1}{r^2} \nabla^2 \Psi_1) - \widetilde{J} (\Psi_1, -\frac{2}{r^3}\partial_r \Psi_1) + \frac{2}{\beta} J(A_1, \frac{1}{r^2}\nabla^2 A_2) + \frac{2}{\beta} J(A_2, \frac{1}{r^2}\nabla^2 A_1) + \frac{4}{\beta} J(A_1, \frac{1}{r^2}\partial_Z\partial_z A_1) \\ 
& + \frac{2}{\beta} J(A_1, -\frac{2}{r^3} \partial_r A_2 ) + \frac{2}{\beta} J(A_2, -\frac{2}{r^3} \partial_r A_1) + \frac{2}{\beta} \widetilde{J} (A_1, \frac{1}{r^2} \nabla^2 A_1) + \frac{2}{\beta} \widetilde{J} (A_1, -\frac{2}{r^3} \partial_r A_1) \\
& + \frac{2}{r} u_1 \partial_z u_2 + \frac{2}{r} u_2 \partial_z u_1 + \frac{2}{r} u_1 \partial_Z u_1 - \frac{2}{\beta}\frac{2}{r} B_1\partial_z B_2 - \frac{2}{\beta}\frac{2}{r} B_2 \partial_z B_1 - \frac{2}{\beta} \frac{2}{r} B_1 \partial_Z B_1
\end{split}
\eeq

\beq
\begin{split}
N_3^u & = -\frac{1}{r}J\left(\Psi_1, u_2\right) - \frac{1}{r}J\left(\Psi_2, u_1\right) - \frac{1}{r}\widetilde{J} \left(\Psi_1, u_1\right) + \frac{1}{r}\frac{2}{\beta} J\left(A_1, B_2\right) + \frac{1}{r} \frac{2}{\beta} J\left(A_2, B_1\right) + \frac{1}{r}\frac{2}{\beta}\widetilde{J}\left(A_1, B_1\right) \\
& - \frac{1}{r^2} u_1\partial_z \Psi_2 - \frac{1}{r^2} u_2 \partial_z \Psi_1 - \frac{1}{r^2} u_1 \partial_Z \Psi_1 + \frac{2}{\beta} \frac{1}{r^2} B_1 \partial_z A_2 + \frac{2}{\beta} \frac{1}{r^2} B_2 \partial_z A_1 + \frac{2}{\beta} \frac{1}{r^2} B_1 \partial_Z A_1
\end{split}
\eeq

\beq
N_3^A = \frac{1}{r} J\left(A_1, \Psi_2\right) + \frac{1}{r}J\left(A_2, \Psi_1\right) + \frac{1}{r} \widetilde{J}\left(A_1, \Psi_1\right)
\eeq

\beq
\begin{split}
N_3^B & = \frac{1}{r} J\left(A_1, u_2\right) + \frac{1}{r} J\left(A_2, u_1\right) + \frac{1}{r}\widetilde{J}\left(A_1, u_1\right) + \frac{1}{r} J\left(B_1, \Psi_2\right) + \frac{1}{r} J\left(B_2, \Psi_1\right) + \frac{1}{r} \widetilde{J} \left(B_1, u_1\right) \\ 
& + \frac{1}{r^2} B_1\partial_z \Psi_2 + \frac{1}{r^2} B_2 \partial_z \Psi_1 + \frac{1}{r^2} B_1 \partial_Z \Psi_1 - \frac{1}{r^2} u_1 \partial_z A_2 - \frac{1}{r^2} u_2 \partial_z A_1 - \frac{1}{r^2} u_1 \partial_Z A_1
\end{split}
\eeq

@@

\bibitem[{Aranson \& Kramer(2002)}]{Aranson:2002}
Aranson, I.S. \& Kramer, L., 2002, RvMP 74, 99

@@

\bibitem[{Balbus \& Hawley(1991)}]{Balbus:1991vs}
Balbus, S A and Hawley, J F, 1991, ApJ 376, 214

@@

\bibitem[{Chandrasekhar(1960)}]{Chandrasekhar:1960wh}
Chandrasekhar, S. 1960, PNAS 46, 253

@@

\bibitem[{Cross \& Hohenberg(1993)}]{Cross:1993el}
Cross, M. C., \& Hohenberg, P. C., 1993, RvMP 65, 851

\bibitem[{Ebrahimi et al.(2009)}]{Ebrahimi:2009ey}
Ebrahimi, F., Prager, S.C., Schnack, D.D, 2009, ApJ 698, 233

@@

\bibitem[{Gissinger et al.(2011)}]{Gissinger:2011td}
Gissinger, C, Ji, H, Goodman, J, 2011, PhRvE 84, 026308

\bibitem[{Gissinger et al.(2012)}]{Gissinger:2012gc}
Gissinger, C, Goodman, J, \& Ji, H, 2012, PhFl 24, 074109

@@

\bibitem[{Hollerbach(2009)}]{Hollerbach:2009ig}
Hollerbach, R., RSPSA 2009, 465, 2107

\bibitem[{Hollerbach \& R\"udiger(2005)}]{Hollerbach:2005tr}
Hollerbach, R. \& R\"udiger, G., 2005, PhRvL 95, 124501

@@

\bibitem[{Ji et al.(2001)}]{Ji:2001kd}
Ji, H, Goodman, J, Kageyama, A, MNRAS 2001, 325, 1

@@

\bibitem[{Kirillov \& Stefani(2013)}]{Kirillov:2013}
Kirillov, O, \& Stefani, F, 2013, PhRvL 111, 061103

\bibitem[{Knobloch \& Julien(2005)}]{Knobloch:2005ba}
Knobloch, E, Julien K, 2005, PhFl, 17, 094106

@@

\bibitem[{Liu et al.(2006)}]{Liu:2006}
Liu, W, Goodman, J, Herron, I, and Ji, H, 2006, PhRvE 74, 056302

\bibitem[{Lopez \& Marques(2005)}]{Lopez:2005} 
Lopez, J.~M., \& Marques, F.\ 2005, PhyD, 211, 168

@@

\bibitem[{Parker \& Krommes(2013)}]{Parker:2013hy}
Parker, J.B. \& Krommes, J.A., 2013, PhPl 20, 100703

@@

\bibitem[{Recktenwald et al.(1993)}]{Recktenwald:1993}
Recktenwald, A., L\"ucke, M., M\"uller, H.W., 1993, PhRvE 48, 4444

\bibitem[{R\"udiger \& Hollerbach(2007)}]{Rudiger:2007}
R\"udiger, G, \& Hollerbach, R, PhRvE 76, 068301

\bibitem[{Schartman et al.(2009)}]{Schartman:2009df}
Schartman, E, Ji, H, Burin, M J, RScI, 2009, 80, 024501

\bibitem[{Shakura \& Sunyaev(1973)}]{Shakura:1973wg}
Shakura, N I and Sunyaev, R A, A\&A, 1973, 24, 337

\bibitem[{Sisan et al.(2004)}]{Sisan:2004ig}
Sisan, D R, Mujica, N, Tillotson, W A, Huang Y-M, Dorland, W, Hassam, A B, Antonsen, T M, Lathrop, D P, PhRvL, 2004, 93, 11

\bibitem[{Stefani et al.(2006)}]{Stefani:2006iv}
Stefani, F, Gundrum, T, Gerbeth, G, R\"udiger, G, Schultz, M, Szklarski, J, Hollerbach, R, PhRvL, 2006, 97, 184502

\bibitem[{Stefani et al.(2009)}]{Stefani:2009hp}
Stefani, F, Gerbeth, G, Gundrum, T, Hollerbach, R, Priede, J, R\"udiger, G, and Szklarski, J, PhRvE, 80, 066303

@@

\bibitem[{Umurhan et al.(2007a)}]{Umurhan:2007dz}
Umurhan, O.M., Regev, O., Menou, K., 2007, PhRvL, 98, 034501

\bibitem[{Umurhan et al.(2007b)}]{Umurhan:2007hs}
Umurhan, O.M., Regev, O., Menou, K., 2007, PhRvE, 76, 036310
